Type Refinements for the Working Class

### 2015-12-19 paper.tex
for lcs, no need to talk about syntax of open terms

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
presheaf $\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
covariant presheaves on $\SCtx\times\Ctx$ of open values, and open bound terms
as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon\parallel\Gamma)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon\parallel\Gamma)\land \exists a. \CanOperators\Pair{\Upsilon}{a}\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon\parallel\Gamma)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{E}{v}}
  }
\end{align*}

We'll write $\Values_\tau(\Upsilon)$ and $\BTms_v(\Upsilon)$ for
$\Values_\tau(\Upsilon\parallel\cdot)$ and $\BTms_v(\Upsilon\parallel\cdot)$
respectively, viewed as covariant presheaves on $\SCtx$. Then, a \emph{lazy
computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an $\SCtx$-indexed
$\equiv_\alpha$-functional evaluation relation
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$ presupposing $\Member{n}{\Naturals}$,
$\Member{M}{\Exprs_\tau(\Upsilon)}$ and $\Member{N}{\Values_\tau(\Upsilon)}$,
expressing that $M$ evaluates to $N$ in $n$ steps.  We will write
$\Eval{\Upsilon}{\tau}{M}{N}$ to mean that there exists an $n$ such that
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$.

>>>>

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished
presheaf $\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
covariant presheaves on $\SCtx$ of closed values, and closed bound terms
as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon)\land \exists a. \CanOperators\Pair{\Upsilon}{a}\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
  }
\end{align*}

Then, a \emph{lazy computation system} (lcs) is a lazy computation language
$\Match{L}{\Pair{\Sigma}{\CanOperators}}$ along with an $\SCtx$-indexed
$\equiv_\alpha$-functional evaluation relation
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$ presupposing $\Member{n}{\Naturals}$,
$\Member{M}{\Exprs_\tau(\Upsilon)}$ and $\Member{N}{\Values_\tau(\Upsilon)}$,
expressing that $M$ evaluates to $N$ in $n$ steps.  We will write
$\Eval{\Upsilon}{\tau}{M}{N}$ to mean that there exists an $n$ such that
$\EvalN{\Upsilon}{\tau}{n}{M}{N}$.
